---
title: "R Introduction Feedback"
author: "Jonathan Mang"
date: "`r Sys.Date()`"
format: html
editor: visual
---

```{r}
#| echo: false
#| include: false

## Set credentials to sign in to REDCap:
# Sys.setenv("REDCAP_API_URL" = "https://your.hospital.org")
# Sys.setenv("REDCAP_API_KEY" = "123456789")


## Install necessary packages:
required_packages <- c("rmarkdown"
                       , "data.table"
                       , "ggplot2"
                       , "tinytex"
                       , "quarto"
                       , "REDCapR")
## Loop over packages and install missing ones:
sapply(
  X = required_packages,
  FUN = function(x) {
    ## only install packages that are not already present:
    if (!x %in% installed.packages()[, "Package"]) {
      install.packages(x)
      return(paste0("Downloaded and installed package '", x, "'."))
    } else {
      return(paste0("Package '", x, "' is already installed."))
    }
  },
  USE.NAMES = TRUE,
  simplify = FALSE
)



## Load the data from REDCap:
col_types <- readr::cols(.default = readr::col_character())

redcap_export <-
  REDCapR::redcap_read(
    redcap_uri = Sys.getenv("REDCAP_API_URL"),
    token = Sys.getenv("REDCAP_API_KEY"),
    col_types = col_types,
    raw_or_label = "label"
  )

stopifnot(redcap_export$success)

data <- redcap_export$data

rm(redcap_export)


## Load the data dictionary to get the meta data of the data:
redcap_dict <-
  REDCapR::redcap_metadata_read(redcap_uri = Sys.getenv("REDCAP_API_URL"),
                                token = Sys.getenv("REDCAP_API_KEY"))

stopifnot(redcap_dict$success)

dict <- redcap_dict$data

rm(redcap_dict)


## Order "Vorwissen":
vorwissen_order <- c("kein Vorwissen",
                     "Grundlagen",
                     "Selbstbewusst",
                     "Expertenwissen")
data$vorwissen <-
  factor(x = data$vorwissen,
         levels = vorwissen_order,
         ordered = TRUE)


## Convert characters to numerics where necessary:
data$zufriedenheit <- as.numeric(data$zufriedenheit)
data$max_dauer_schulung <- as.numeric(data$max_dauer_schulung)


### Add "Themen" labels:
## Get labels from data dictionary:
# labels <-
#   data.table::as.data.table(dict)[field_name == "themen", select_choices_or_calculations]
# 
# ## Separate the labels from each other (all are in one long string):
# labels <- strsplit(x = labels, split = " | ", fixed = TRUE)
# 
# ## Remove the prefix number:
# labels <- gsub(pattern = "^(*).(, )",
#      replacement = "",
#      x = labels[[1]])
# labels <- data.table::as.data.table(labels)
# labels[, "id" := seq.int(length(labels))]



## Plot defaults:
library(ggplot2)
theme_set(theme_bw())  # pre-set the bw theme.



```

## Introduction

A high level of satisfaction is elementary for good receptivity. In order to estimate the satisfaction of the participants, a possibility should be created to reproducibly determine the satisfaction of the participants.

## Methods

REDCap was used to create user satisfaction questionnaires and collect user feedback in the form of a survey.

## Results

```{r}
#| echo: false

data <- data.table::as.data.table(data)
# data[,.SD, .SDcols = c("vorwissen", "zufriedenheit")]
best_zufriedenheit_class <- min(data$zufriedenheit)
best_zufriedenheit <-
  data[zufriedenheit == best_zufriedenheit_class,][, by = vorwissen, .N][order(N, decreasing = T), ]
best_zufriedenheit_n <- best_zufriedenheit[[1,"N"]]

```

`r nrow(data)` people participated in the survey.
The group of participants with the previous knowledge "`r best_zufriedenheit[[1,"vorwissen"]]`" have thereby evaluated the training most positively.

### User feedback

```{r}
#| echo: false
#| label: fig-training-satisfaction
#| fig-cap: "Q: How satisfied were you with the training you received?"
#| warning: false


library(ggplot2)

# plot(data$zufriedenheit)

ggplot(data = data,
       mapping = aes(x = zufriedenheit, fill = vorwissen)) + geom_histogram(stat = "count") +
  xlab("Zufriedenheit (1 = sehr zufrieden; 5 = sehr unzufrieden)") +
  ylab("Anzahl") +
  # xlim(c(1, 5)) +
  guides(fill = guide_legend(title = "Vorwissen"))


```

```{r}
#| echo: false
#| label: fig-training-max-duration
#| fig-cap: "Q: What is the maximum duration of an R training course?"
#| warning: false
#| fig-width: 5
#| fig-height: 3

# plot(data$max_dauer_schulung)

ggplot(data, aes(y = max_dauer_schulung)) + geom_boxplot(varwidth=TRUE) +
  labs(y="Maximale Dauer der Schulung [h]"
       # x="", 
       # title="Scatterplot with overlapping points", 
       # caption="Source: midwest"
       )


```

## Discussion

All well and good, but how can R and the knowledge of the need for reproducible research now concretely improve your daily research routine?


